### 2020-12-13 ch02_scientific_background/scientific_background.tex
Added section description for section on reducing uncertainties

\section{Techniques to Reduce Uncertainties in Multi-Model Climate Projections}
\label{sec:02:techniques_to_reduce_uncertainties}

As shown in \cref{subsec:02:source_of_uncertainties}, projections of the future
climate are always associated with uncertainties. In the context of this
thesis, the most relevant source for these is the climate response uncertainty.
It originates from the different responses of the different climate models in a
multi-model ensemble to a given forcing and affects all multi-model projections
of the future climate (\eg{} the climate sensitivity or the future development
of the global carbon cycle). This section introduces three state-of-the-art
techniques to reduce uncertainties in multi-model climate model projections
with observations. The presented methods form the baseline for the work
presented in this thesis.

@@

>>>>

\section{Techniques to Reduce Uncertainties in Multi-Model Climate Projections
  with Observations}
\label{sec:02:techniques_to_reduce_uncertainties}

As shown in \cref{subsec:02:source_of_uncertainties}, projections of the future
climate are always associated with uncertainties. In the context of this
thesis, the most relevant source of uncertainty is the climate response
uncertainty. It originates from our imperfect knowledge on how the climate
system will respond to external forcing. In a multi-model ensemble (\eg{} from
\ac{CMIP}), this is expressed as the different responses of the different
climate models to a given forcing. A common approach to distill information
about a projected quantity from multi-model ensembles is to treat the
unweighted \ac{MMM} and the multi-model range as best estimate and uncertainty
measure of this quantity \autocite{Collins2013}. This \emph{one model one vote}
or \emph{model democracy} approach basically assumes that all climate models
are independent, equally plausible, distributed around reality and that the
projected multi-model range is representative for the uncertainty in the
projected quantity \autocite{Knutti2017a}. However, since the \ac{CMIP}
ensembles, sometimes referred to as \emph{ensembles of opportunity}, have not
been designed to represent a true statistical sample of the reality composed of
independent climate models \autocite{Tebaldi2007}, these assumptions do not
hold in practice. The main reasons for this are that different climate models
(even for different modeling institutions) share parts of their code
\autocite{Knutti2013}, that models do not equally well represent the observed
past and present-day climate \autocite{Knutti2013} and that models might suffer
from common structural limitations like missing processes
\autocite{Knutti2017a}.

Thus, more sophisticated techniques are necessary to evaluate multi-model
climate projections. This section introduces three state-of-the-art methods to
assess multi-model projections and reduce associated uncertainties with
observations. These techniques form the baseline of the work presented in the following chapters.

@@

From Knutti (2017): A way out, at least partially, is to reframe the
competition of “which model is the best” to “which models are adequate for
predicting X” [Parker, 2009]
